Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
small edits

\Cref{fig:toy_causal_sample} shows the results for fitting the GPCM and CGPCM to instead a \textit{noiseless} random sample from the CGPCM. Since the drawn filter $h$ satisfies $|h(0)|>0$, the sample is rough and thus appears noisy. The challenge for the models is to not mistake this sample roughness for observation noise. Observe that the CGPCM fits the filter $h$ and kernel $k_{f \cond h}$ well, whereas GPCM's fit is mediocre. Despite roughly getting the correlation structure right, the GPCM mistakes the sample roughness for observation noise and provides a poor fit of the function $f\cond h$. The CGPCM, on the other hand, correctly recognises the sample roughness and provides an excellent fit of $f \cond h$. This discrepancy is explained by inspecting the fit of the PSD: the GPCM is unable to fit the higher frequencies in the sample, whereas the CGPCM does so succesfully; this is consistent with the priors depicted in \cref{fig:prior_psd}.

>>>>

\Cref{fig:toy_causal_sample} shows the results for fitting the GPCM and CGPCM to instead a \textit{noiseless} random sample from the CGPCM. Since the drawn filter $h$ satisfies $|h(0)|>0$, the sample is rough and thus appears noisy. The challenge for the models is to not mistake this sample roughness for observation noise. Observe that the CGPCM fits the filter $h$ and kernel $k_{f \cond h}$ well, whereas GPCM's fit is mediocre. Despite approximately capturing the correlation structure, the GPCM mistakes the sample roughness for observation noise and provides a poor fit of the function $f\cond h$. The CGPCM, on the other hand, correctly recognises the sample roughness and provides an excellent fit of $f \cond h$. This discrepancy is explained by inspecting the fit of the PSD: the GPCM is unable to fit the higher frequencies in the sample, whereas the CGPCM does so succesfully; this is consistent with the priors depicted in \cref{fig:prior_psd}.
